Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-31 paper.tex
Updates in simulations, still work in progress

\todo{Make more simulations to support that claim.}
After running a few simulations, we saw that the comparison between
Cluster reads and Multiple reads essentially depends on the three
Cluster reads configurations.  When Cluster reads merge incomplete
block rows (case 1), they are always outperformed by Multiple reads.
When Cluster reads merge complete block rows (case 2), the comparison
between Cluster reads and Multiple reads depends on the values of $D$
and $n$. Figure~\ref{fig:model-comparison} shows two situations where
Cluster reads and Multiple reads are alternatively better than each
other. When Cluster reads merge complete block slices (case 3),
Cluster reads and Multiple reads are equivalent.

\begin{figure}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain.pdf}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-rescan.pdf}
  \caption{Number of seeks for Cluster reads vs Multiple reads when
    Cluster reads merge complete block rows (case 2), for D=3000 and
    b=2. Left: n=125; Right: n=64,000.}
  % Gnuplot file: scripts/model/model.gnplt
  \label{fig:model-comparison}
\end{figure}

@@

@@

\section{Results}
\label{sec:results}

>>>>

@@

\todo{Make more simulations to support that claim.}

After running a few simulations, we saw that the comparison between
Cluster reads and Multiple reads essentially depends on the three
Cluster reads configurations.  When Cluster reads merge incomplete
block rows (case 1), they are always outperformed by Multiple reads.
When Cluster reads merge complete block rows (case 2), the comparison
between Cluster reads and Multiple reads depends on the values of $D$
and $n$. Figure~\ref{fig:model-comparison} shows two situations where
Cluster reads and Multiple reads are alternatively better than each
other. When Cluster reads merge complete block slices (case 3),
Cluster reads and Multiple reads are equivalent.

\begin{figure}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-creads.pdf}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-mreads.pdf}
  \caption{Number of seeks for Cluster reads (Left) and Multiple reads (Right), for
    D=3000, b=2 and n=125.}
  % Gnuplot file: scripts/model/model.gnplt
  \label{fig:model-individual}
\end{figure}

\begin{figure}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison.pdf}
  \includegraphics[width=0.45\columnwidth]{figures/model-big-brain-comparison-moreblocks.pdf}
  \caption{Number of seeks for Cluster reads vs Multiple reads when
    Cluster reads merge complete block rows (case 2), for D=3000 and
    b=2. Left: n=125; Right: n=64,000.}
  % Gnuplot file: scripts/model/model.gnplt
  \label{fig:model-comparison}
\end{figure}

\section{Experiments}
\label{sec:results}

@@
